SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-13 frontrunning/Latex/main.tex
some other edits
Still could not understand Malinova/Park summary, so fixed
[frontrunning] batch auctions + authors + WIP watermark
[frontrunning] Fix affiliate + comments about cryptokitties
Add notes from meeting on Feb 5th
[frontrunning] uncomment Acknowledgements

\title{The paper on blockchain front-running}
\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}

\institute{
	Gina Cody School of Engineering and Computer Science\\ Concordia University
	}

@@

\clearpage
\bibliography{bib/Frontrunning_Ref}
%\nocite{*}

>>>>

\title{SoK: Transparent Dishonesty: front-running attacks on Blockchain.}
\author{}

\author{
	Shayan Eskandari\inst{\dag\ddag},
	Seyedehmahsa Moosavi\inst{\dag},
	Jeremy Clark\inst{\dag}
	}

\institute{
	\textsuperscript{\dag} Gina Cody School of Engineering and Computer Science\\ Concordia University \\
	\textsuperscript{\ddag} ConsenSys Diligence
	}

@@

\bibliography{bib/Frontrunning_Ref}
%\nocite{*}
